Figures to insert in text

### 2018-03-07 Chapters/sdm2.tex

A member of my Master's committee, professor Paulo Murilo\footnote{Universidade Federal Fluminense's physicist doctor Paulo Murilo}, has proposed a generalized reading operation (personal communication), which covers both Kanerva's and Chada's read --- and opens a new venue of potential discoveries. He proposed summing all hard-location counters raised to the power of $z$ while holding the original sign of the counter (positive or negative). Thus, Kanerva's read would be the same as $z=1$, while Chada's would be the same as $z=0$. Hence, we will here explore how SDM would behave with other values of $z$, such as 0.5, 2, and 3. Mathematically, let $A$ be the set of the counters of the activated hardlocation, and $c_i$ be the counter of the $i$-th bit. Then,

>>>>

A member of my Master's committee, Prof. Paulo Murilo\footnote{Universidade Federal Fluminense's Physics Professor Paulo Murilo}, has proposed a generalized reading operation (personal communication), which covers both Kanerva's and Chada's read --- and opens a new venue of potential discoveries. He proposed summing all hard-location counters raised to the power of $z$ while holding the original sign of the counter (positive or negative). Thus, Kanerva's read would be the same as $z=1$, while Chada's would be the same as $z=0$. Hence, we will here explore how SDM would behave with other values of $z$, such as 0.5, 2, and 3. Mathematically, let $A$ be the set of the counters of the activated hardlocation, and $c_i$ be the counter of the $i$-th bit. Then,
